Usage metrics

### 2021-04-11 analysis/environments.Rmd
Environemnt high-level classification

@@

overview_table(
  r("nb null envir", nb_null),
  r("nb null envir sites", nb_null_sites),
  r("nb null envir site percent", ratio(nb_null_sites, nb_eval_calls))
)
```

>>>>

# Caller environments

```{r}
caller_envs <- env_calls %>% filter(!is.na(hierarchy), is.na(specific_env))
nb_caller_env_sites <- caller_envs %>% pull(src_ref) %>% n_distinct()

overview_table(
  r("nb caller env sites", nb_caller_env_sites),
  r("caller env site percent", ratio(nb_caller_env_sites, nb_call_sites))
)
```

# New environments

```{r}
new_envs <- env_calls %>% filter(!is.na(new_env))
nb_new_env_sites <- new_envs %>% pull(src_ref) %>% n_distinct()

overview_table(
  r("nb new env sites", nb_new_env_sites),
  r("new env site percent", ratio(nb_new_env_sites, nb_call_sites))
)
```

@@

overview_table(
  r("nb null envir", nb_null),
  r("nb null envir sites", nb_null_sites),
  r("nb null envir site percent", ratio(nb_null_sites, nb_call_sites))
)
```

### 2021-04-11 analysis/usage.Rmd
Environemnt high-level classification

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/base/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---
